COG-ED Manuscript

### 2021-08-16 06_Paper/COG-ED/Manuscript.Rmd
Tried file import
Cannot access subfolder

>>>>

```{r}

library(here)         # to set a directory without defined paths
library(tidyverse)    # plotting and managing data

# set top level directory to source file
here::i_am("Manuscript.Rmd")

# import n-back data into a list
datalist_nback = lapply(list.files(pattern = "nback.*csv"), read.csv(here("Sampledata")), stringsAsFactors = FALSE, header = TRUE)

```
